A meta-analysis of the impacts of best management practices on nonpoint source pollutant concentration.

### 2024-05-23 frontiers_submission/reviewer_response/reviewer_response.qmd

---
title: "Response to reviewer comments"
format:
  hikmah-response-typst: default
---

Thank you for giving us the opportunity to revise our manuscript. Reviewer comments were especially constructive and have improved the manuscript. The Reviewers' comments are cited or summarized in [red italicized text]{.memo-reviewer-inline}, and our responses are in black Roman text. We include excerpts from our revised manuscript in [blue]{.memo-excerpt-inline}.

# Reviewer 2

::: {.memo-reviewer}
***Reviewer 2***: The reported work only used BMP category and large-scale 
spatial indicators as predictors of their performance, but the parameters of 
BMPs (e.g., the size of infiltration) are missing. This may be why the model 
has a high variance.
:::

We generally found that specific BMP parameters such as infiltration size, 
drainage area, infiltration media/soil types, and other factors relevant to BMP 
performance were not well reported across studies. 
Our characterization of BMPs is further complicated by inclusion of BMPs that
rely on completely different pollutant removal or prevention mechanisms. 
For example, nutrient management BMPs do not rely on a infiltration area
and we would not be able to include these types of management BMPs if 
infiltration size were a regression moderator.
This is certainly a limitation of the study, but the purpose of the project
is a broad scale look at BMPs. Further studies investigating specific BMP types
with common removal mechanisms are certainly appropriate. 
To address the Reviewer's concerns, we have added the following to the Discussion:

::: {.memo-excerpt}
Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?
:::

---

::: {.memo-reviewer}
***Reviewer 2***: The heterogeneity of FIB, TN, TP, TSS are high, the study 
require subgroup analysis or sensitivity analysis on this issue.
:::

I appreciate this comment, but want to caution against extensive subgroup 
analysis/sensitivity analysis. While heterogeneity was indeed high, 
the primary purpose of the meta-regression models are to investigate how much
of the variance that a set of pre-determined moderators explain. Meta-regression
were conducted in lieu of traditional subgroup analysis. While additional 
subgroup analysis could be conducted based on additional moderators, we risk 
conducting a "data-dredging" study.

::: {.memo-excerpt}
Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem.
:::

# Reviewer 3

::: {.memo-reviewer}
***Reviewer 3***: Is there any moderating effects of study area size or scale (i.e., field, farm, and watershed) and urban versus agricultural source on the performance of BMPs?
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  What is the temporal coverage of the aridity index? Does it reflect long-term climate patterns or only a single year? Using a snapshot of the climate variable would be less optimal.
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Since the locations of the studies are not precisely defined in many cases, please provide more details on how to spatially link studies to the aridity index map to obtain aridity values.
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Have you examined the effects of soil biophysical properties in addition to aridity? Can you obtain more detailed spatial locations of the various studies so to link these studies to local soil conditions in addition to climate?
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Could you please elaborate more on the topic “scaling BMP pollutant reductions to basin wide water quality improvement remains a substantial challenge”. This is a very interesting point, what modeling or mixed approaches exist to achieve this goal?
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Please expand the abbreviation “ROSES” in the main text.
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Change “Standard deviation of control measreuments” to “… measurements” in Table 2.
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Change “and outlier” to “an” in Figure S9 to S14.
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  In the sentence "Any study values outside of the full model confidence intervals would be considered an outlier.", by “study values”, do you mean the intercept estimate of a study?
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Explain the abbreviated parameters in Figure 1 – 5 (e.g. TS, TP, TN, etc.)
:::

Added definitions to all the figure captions.

---

::: {.memo-reviewer}
***Reviewer 3***:   Delete one of the “the” at line 277.
:::

Fixed.

# Reviewer 5

::: {.memo-reviewer}
***Reviewer 5***:   Add spatial extent covered in abstract
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Add sediments or suspended sediments to keywords if there is space
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   1st Paragraph of introduction (Line 28), add a sentence about sediment impairments to waters similar to the ones discussing FIBs and nutrients impairments
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Include small paragraph in discussion about how search terms of “BMPs” or “best management practices” and inclusion criteria (concentrations) may have not captured some studies. For example, if the study used the name of the practice instead of BMP. Also, there are a suite of agricultural drainage practices but studies generally focus on load reduction (from flow reduction) compared to concentration reduction (see Frankenberger et al., 2023 https://elibrary.asabe.org/abstract.asp?aid=54314 who’s review has a cluster of those studies in the Midwest, which is blank on this map). 
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Lines 61 – 64 consider adding an example BMP for instances where effluent is and is not related to influent concentration
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Line 136 – specify version of R used
:::

Added.

---

::: {.memo-reviewer}
***Reviewer 5***:   Line 149 – check for consistency in defining equation terms (CV v. CV2) 
:::

Fixed. Now reads as below:

::: {.memo-excerpt}
$$
v(ROM) = \frac{\sum_{i=1}^{K}{(CV^2_{control,i})/K}}{n_{control}} + \frac{\sum_{i=1}^{K}{(CV^2_{experiment,i})/K}}{n_{experiment}},
$$

where *v* represents the sampling variance, $CV^2_{control,i}$ and $CV^2_{experiment,i}$ are the squared coefficients of variation from the *i*th study for studies 1, 2, ..., *K*.
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Line 160 – mean annual potential (or reference) evapotranspiration
:::

Fixed.

---

::: {.memo-reviewer}
***Reviewer 5***:   Line 191 – “published after between 1999 and 2023” confusing wording, 2000-2022?
:::

Fixed.

---

::: {.memo-reviewer}
***Reviewer 5***:   Line 194 – PO~4
:::

Fixed.

---

::: {.memo-reviewer}
***Reviewer 5***:   Lines 213 – 214 – clarify “may not be reliable” in general, or just for lower aridity?
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Lines 61 – 64 consider adding an example BMP for instances where effluent is and is not related to influent concentration
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Lines 242-254: Nice discussion on spatial coverage with the caveat that we are not aware of the actual distribution of BMPs. However, I am curious, are BMPs over-represented or just predominately located in humid regions? Could it be related to larger population concentrations along the humid east coast than the arid west? Are detention practices common in locations with little rainfall and high potential loss of water to evaporation? See my recommendation for Figure 7 to potentially add a 3rd distribution of aridity index of urban & agricultural land covers across the US. 
:::

---

::: {.memo-reviewer}
***Reviewer 5***:  Lines 349 – 351: Based on your experience trying to synthesis information across studies in this review process, do you have recommendations for minimum reporting requirements or standards for future studies on BMP concentration reductions? If so, please list in text or perhaps in a box. 
:::

---

::: {.memo-reviewer}
***Reviewer 5***:   Consider defining abbreviated terms in the figure caption for clarity (e.g, DIN, FIB)
:::

We have added terms to all the figure captions.

---

::: {.memo-reviewer}
***Reviewer 5***:  Table 1
- Excluision Criteria → Exclusion Criteria
- Under Inclusion Criteria/Outcomes include sediments in addition for FIB and nutrients
- Under Exclusion criteria/Outcomes “Studies not explicitly linking reductions to a specific BMP…” it may be more clear if you say linking “concentration reductions”
:::

---

::: {.memo-reviewer}
***Reviewer 5***:  Figure 1
- While the color palette may be appropriate for normal, trichromatic, and dichromatic conditions there is very little contrast in the monochromatic or grey-scale view. If article is laser printed or photocopied, it is difficult to distinguish between the stacked elements of the bar graphs. Maybe white or black outline separating stacked sections could help.
- Please increase the length of the y-axis for panel C to for larger font size/less crowding
:::

---

::: {.memo-reviewer}
***Reviewer 5***:  Figure 3
- Consider adjusting the background grey value for no-data in maps. In grey-scale/monochromatic view the mid-tone greens are indistinguishable from the no-value grey. Labeling the states with the number of studies does help.
:::

We changed to a transparent background for states with no data.

---

::: {.memo-reviewer}
***Reviewer 5***:  Figure 4, 5, 6
- Consider adding including the range in sampling variance in the caption or provide a visual key to demonstrate the values represented by differently sized points. 
:::

---

::: {.memo-reviewer}
***Reviewer 5***:  Figure 5
- Add panel letters to figure caption to improve clarity.
- Consider adding note for aridity index (annual precipitation/potential evapotranspiration) in the x-label or in the figure caption that higher values indicate more humid conditions.
:::

Thank you for the suggestions. We have incorporated all the suggestions to the 
figure.

---

::: {.memo-reviewer}
***Reviewer 5***:  Figure 7
- It is difficult to see the tail of the US. Aridity Index values, consider having a slight offset from zero above the x-axis/y-axis intercept.
- Consider having a 3rd distribution shown – U.S. Aridity Index Values for urban and agricultural lands, with other land-covers filtered out, if these are the land-cover types that are associated with the placement of BMPs you analyzed. You could use a product with the same resolution as your Aridity Index values such as the 30m National Land Cover Database (https://www.usgs.gov/centers/eros/science/national-land-cover-database#overview )
- Consider adding note for aridity index (annual precipitation/potential evapotranspiration) in the x-label or in the figure caption that higher values indicate more humid conditions.
:::

Thank you for the suggestions. We have incorporated all the suggestions to the 
figure. 
We switched from overlapping densities to a ridge plot with each category labeled
on the y-axis since it gets difficult to discern densities with three overlapping
plots.

### 2024-05-23 frontiers_submission/frontiers_submission_revision_01.Rmd
working on responses

Results from each database were first filtered to remove duplicates.
After removal of duplicates, each member of the research team (*n* = 4) was assigned a subset of studies to evaluate if they should be included (Table \@ref(tab:criteria)).
Each study was reviewed by two team members and differences in opinion were collectively discussed and agreed upon before progressing.
The remaining studies were split among team members for data extraction (Table \@ref(tab:datvars)), again with at least two team members reviewing each study. 
If data was provided in figures, the data was extracted with the WebPlotDigitizer tool [@rohatgiWebPlotDigitizer2022]. 
Searches, review, and data extractions were conducted separately for FIB and nutrient related parameters.
See Figure S1 and S2 for ROSES diagram. BMP data from the systematic review is available in @kikoyoTWRINPSBMPDB2024.

@@

tibble(Variable = c(
  "Publication Year", "Parameter", "Runoff source", "Source type",
  "BMP", "BMP Classification", "BMP Category", "BMP Subcategory",
  "Study scale", "Location", "State", "Study area", "Longitude", "Latitude",
  "Study years", "N control", "N experiment", "X control", "X experiment", 
  "SE control", "SE experiment", "Minimum control", "Minimum experiment", 
  "Maximum control", "Maximum experiment", "SD control", "SD experiment",
  "Units", "Percent reduction"),
  Description = c("Year the study was published",
                  "The specific pollutant measured",
                  "Dominant source of runoff (crop fields, livestock pasture, commerical, residential)",
                  "Major categorization of runoff source: agricultural or urban",
                  "BMP evaluated",
                  "BMP description based on NRCS conservation practice standards and EPA BMP fact sheets",
                  "BMP categorization based on structural or management",
                  "BMP subcategorization based on pollutant removal processes",
                  'Spatial scale of the study area (lot/field, community, watershed)',
                  "Location name used in the study description",
                  "State where the study was conducted",
                  "Drainage area in hectares",
                  "Approximated or reported latitude coordinate",
                  "Approximated or reported longitude coordinate",
                  "Year or years when data were collected",
                  "Number of control measurements",
                  "Number of experiemental measurements",
                  "Mean concentration for control measurements",
                  "Mean concentration for experiemental measurements",
                  "Standard error of control measurements",
                  "Standard error of experimental measurements",
                  "Minimum control measurement",
                  "Minimum experiment measurement",
                  "Maximum control measurement",
                  "Maximum experiment measurement",
                  "Standard deviation of control measreuments",
                  "Standard deviation of experimental measurements",
                  "Units reported by the study",
                  "BMP efficiency for studies that only reported efficiency")
) |> 
  kableExtra::kbl(booktabs = TRUE,
                  caption = "Study and effect variables extracted for review.") |> 
  kableExtra::kable_styling(full_width = FALSE) |>
  kableExtra::column_spec(1, width = "10em") |> 
  kableExtra::column_spec(2, width = "25em")

@@

We used the "rma.mv" function in the *metafor* R package to fit multilevel random effects regression models with *ROM* as the effect variable [@viechtbauerConductingMetaanalysesMetafor2010; @rcoreteamLanguageEnvironmentStatistical2023].
We fit separate models for FIB, total nitrogen (TN), dissolved inorganic nitrogen (DIN), total phosphorus (TP), orthophosphate (PO~4~), and total suspended sediment (TSS).
Our models specified a nested random effects term accounting for heterogeneity between effect sizes from the same study and for heterogeneity between studies.
*ROM* was used as the effect size which required the exclusion of studies that only provided measures of BMP efficiency and not the underlying data used to derive the metric.
A key feature of meta-analysis is the weighting of effects using sampling variance of individual effect sizes.
`r percent_missing |> xfun::numbers_to_words(cap = TRUE)` percent of `r total` effect sizes were missing standard deviations required to estimate sampling variance. 
Removal of studies due to missing variance information can introduce substantial bias [@kambachConsequencesMultipleImputation2020]. 
Missing standard deviations were imputed using the pooled ratio of the mean effect size to coefficient of variation (CV) [@brackenStatisticalMethodsAnalysis1992].
Sampling variance was estimated utilizing the average squared CV across all studies divided by sample size for each effect [@nakagawaRobustReadilyImplementable2023; @doncasterCorrectionBiasMeta2018]:

@@

where *v* represents the sampling variance, $CV_{control,i}$ and $CV^2_{experiment,i}$ are the coefficients of variation from the *i*th study for studies 1, 2, ..., *K*. *n~control~* and *n~experiment~* are the number of samples in the control (pre-treatment) trial or experimental (post-treatment) trial respectively.

Our initial models included log transformed influent concentration, BMP subcategory (drainage modification, crop field management, livestock management, filtration, treatment, detention, or infiltration), aridity index (mean-centered), influent concentration\texttimes BMP subcategory interactions, and aridity index\texttimes BMP subcategory interactions were included as fixed effect terms.
Aridity index was the only moderator not obtained directly in the systematic review (Table \@ref(tab:datvars)).
We mapped study location coordinates to aridity index values published in the "Global Aridity Index and Potential Evapotranspiration Database - Version 3" (Global-AI_PET_v3) which provides gridded 30 arc-second annual average precipitation and potential evapotranspiration estimates [@zomerVersionGlobalAridity2022].
The aridity index is calculated as the ratio of mean annual precipitation to mean annual evapotraspiration with values between 0 and 0.5 considered hyper to semi-arid, and values above 0.65 as humid.

@@

Our systematic review identified a total of 33 studies and 125 effect sizes on FIB, 24 studies and 50 effect sizes on TN, 31 studies and 88 effect sizes for DIN, 31 studies and 61 effect sizes for TP, 17 studies and 36 effect sizes for PO~4~, and 33 studies with 125 effect sizes for TSS. 
The majority of studies were identified as smaller scaled lot or field studies (Figure \@ref(fig:bmpsummary) A).
FIB studies had a roughly equal proportion of large watershed/catchment studies and studies conducted at the community/farm scale or smaller.
We also identified that the majority of studies (all parameters) were conducted on urban or non-agricultural runoff (Figure \@ref(fig:bmpsummary) B).
We did identify a wide variety of BMPs in the review, but it did not appear that any particular type of BMP was responsible for the majority of studies for any given parameter (Figure \@ref(fig:bmpsummary) C).
Our review was restricted to studies published after between 1999 and 2023.
The number of studies published for each parameter were roughly uniformly distributed over time (Figure \@ref(fig:bmptemporal) A) and are not indicative of increases or decreases in the number of published studies.
Study length was strongly skewed for all parameters (Figure \@ref(fig:bmptemporal) B). Median study lengths were 3 (DIN), 2 (FIB), 2.5 (PO~4), 2.5 (TN), 2.5 (TP), and 2 (TSS) years. 
There appears to be a strong clustering of BMP studies in the mid-Atlantic region (North Carolina, Virginia, Maryland) with other states sparsely represented or completely absent from the review (Figure \@ref(fig:studymap)).

@@

Study design prevented us from properly assessing BMP effectiveness as a function of age.
Conducting a meta-analysis of BMP effectiveness over time is hampered both by the lack of long-term studies and lack of standardized reporting mechanisms.
Some studies simply describe the change in pollutant concentrations or loads at the beginning and end of the study as a percent change [@haileHydraulicPerformancePollutant2016] which presents statistical problems, especially when sampling variance is not reported.
Changes in performance can also be described using a linear regression using date (transformed as a numeric variable) as an independent variable and log-transformed water quality as the dependent variable [@mitschCreatingWetlandsPrimary2012; @mitschValidationEcosystemServices2014; @pausAssessmentHydraulicToxic2014].
Slopes are a valid effect size for use in meta-analysis but the set of covariates used between studies should be the same since the coefficient of interest is adjusted to account for other terms in the the regression model [@beckerSynthesisRegressionSlopes2007].
It would be reasonable to assume that regressions equations vary between studies to adjust results for seasonality, flow rates, and other variables.
Future efforts for assessing the performance of BMPs over time would benefit not only from more studies, but a more standardized method for providing comparable results.

@@

Raw data from the systematic review is deposited on Zenodo: https://zenodo.org/doi/10.5281/zenodo.8302472.
R code used in the analysis is also deposited on Zenodo: TBD.

@@

```{r bmpsummary}
#| fig.cap: "Summary of (A) study scale, (B) dominant runoff source, and (C) BMPs identified in the systematic review."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r bmptemporal}
#| fig.cap: "Number of studies identified in the systematic review summarized by (A) publication date and (B) study length."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r studymap}
#| fig.cap: "Distribution of studies identified in the systematic review by state and parameter."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r overalleffect}
#| fig.cap: "Estimated effect sizes and intervals from the intercept only multilevel random effects model. Individual points represent studies, with size scaled by sampling variance. The point estimate with uncertaintity bars indicate the estimated overall effect, 95% confidence intervals, and 95% prediction intervals. Here, \\textit{k} indicates the number of overall effects with the number of unique studies in parenthesis."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r fibeffect}
#| fig.cap: "Predicted marignal effect of influent FIB and aridity index (conditioned on BMP subcategory). Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r phoseffect}
#| fig.cap: "Predicted marignal effect of influent pollutant concentration on TP (Panel A) and PO\\textsubscript{4} (Panel B) reductions. Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r aiindex}
#| fig.cap: "Comparison of the relative distributions (density) of aridity index values across the U.S. against aridity index values for studies in the systematic review."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "50%"

>>>>

Results from each database were first filtered to remove duplicates.
After removal of duplicates, each member of the research team (*n* = 4) was assigned a subset of studies to evaluate if they should be included (Table \@ref(tab:criteria)).
Each study was reviewed by two team members and differences in opinion were collectively discussed and agreed upon before progressing.
The remaining studies were split among team members for data extraction (Table \@ref(tab:datvars)), again with at least two team members reviewing each study. 
If data was provided in figures, the data was extracted with the WebPlotDigitizer tool [@rohatgiWebPlotDigitizer2022]. 
Searches, review, and data extractions were conducted separately for FIB and nutrient related parameters.
See Figure S1 and S2 for RepOrting standards for Systematic Evidence Syntheses 
(ROSES) diagram. 
BMP data from the systematic review is available in @kikoyoTWRINPSBMPDB2024.

@@

tibble(Variable = c(
  "Publication Year", "Parameter", "Runoff source", "Source type",
  "BMP", "BMP Classification", "BMP Category", "BMP Subcategory",
  "Study scale", "Location", "State", "Study area", "Longitude", "Latitude",
  "Study years", "N control", "N experiment", "X control", "X experiment", 
  "SE control", "SE experiment", "Minimum control", "Minimum experiment", 
  "Maximum control", "Maximum experiment", "SD control", "SD experiment",
  "Units", "Percent reduction"),
  Description = c("Year the study was published",
                  "The specific pollutant measured",
                  "Dominant source of runoff (crop fields, livestock pasture, commerical, residential)",
                  "Major categorization of runoff source: agricultural or urban",
                  "BMP evaluated",
                  "BMP description based on NRCS conservation practice standards and EPA BMP fact sheets",
                  "BMP categorization based on structural or management",
                  "BMP subcategorization based on pollutant removal processes",
                  'Spatial scale of the study area (lot/field, community, watershed)',
                  "Location name used in the study description",
                  "State where the study was conducted",
                  "Drainage area in hectares",
                  "Approximated or reported latitude coordinate",
                  "Approximated or reported longitude coordinate",
                  "Year or years when data were collected",
                  "Number of control measurements",
                  "Number of experiemental measurements",
                  "Mean concentration for control measurements",
                  "Mean concentration for experiemental measurements",
                  "Standard error of control measurements",
                  "Standard error of experimental measurements",
                  "Minimum control measurement",
                  "Minimum experiment measurement",
                  "Maximum control measurement",
                  "Maximum experiment measurement",
                  "Standard deviation of control measurements",
                  "Standard deviation of experimental measurements",
                  "Units reported by the study",
                  "BMP efficiency for studies that only reported efficiency")
) |> 
  kableExtra::kbl(booktabs = TRUE,
                  caption = "Study and effect variables extracted for review.") |> 
  kableExtra::kable_styling(full_width = FALSE) |>
  kableExtra::column_spec(1, width = "10em") |> 
  kableExtra::column_spec(2, width = "25em")

@@

We used the "rma.mv" function in the *metafor* R package (R version 4.3.1) to fit multilevel random effects regression models with *ROM* as the effect variable [@viechtbauerConductingMetaanalysesMetafor2010; @rcoreteamLanguageEnvironmentStatistical2023].
We fit separate models for FIB, total nitrogen (TN), dissolved inorganic nitrogen (DIN), total phosphorus (TP), orthophosphate (PO~4~), and total suspended sediment (TSS).
Our models specified a nested random effects term accounting for heterogeneity between effect sizes from the same study and for heterogeneity between studies.
*ROM* was used as the effect size which required the exclusion of studies that only provided measures of BMP efficiency and not the underlying data used to derive the metric.
A key feature of meta-analysis is the weighting of effects using sampling variance of individual effect sizes.
`r percent_missing |> xfun::numbers_to_words(cap = TRUE)` percent of `r total` effect sizes were missing standard deviations required to estimate sampling variance. 
Removal of studies due to missing variance information can introduce substantial bias [@kambachConsequencesMultipleImputation2020]. 
Missing standard deviations were imputed using the pooled ratio of the mean effect size to coefficient of variation (CV) [@brackenStatisticalMethodsAnalysis1992].
Sampling variance was estimated utilizing the average squared CV across all studies divided by sample size for each effect [@nakagawaRobustReadilyImplementable2023; @doncasterCorrectionBiasMeta2018]:

@@

where *v* represents the sampling variance, $CV^2_{control,i}$ and $CV^2_{experiment,i}$ are the squared coefficients of variation from the *i*th study for studies 1, 2, ..., *K*. *n~control~* and *n~experiment~* are the number of samples in the control (pre-treatment) trial or experimental (post-treatment) trial respectively.

Our initial models included log transformed influent concentration, BMP subcategory (drainage modification, crop field management, livestock management, filtration, treatment, detention, or infiltration), aridity index (mean-centered), influent concentration\texttimes BMP subcategory interactions, and aridity index\texttimes BMP subcategory interactions were included as fixed effect terms.
Aridity index was the only moderator not obtained directly in the systematic review (Table \@ref(tab:datvars)).
We mapped study location coordinates to aridity index values published in the "Global Aridity Index and Potential Evapotranspiration Database - Version 3" (Global-AI_PET_v3) which provides gridded 30 arc-second annual average precipitation and potential evapotranspiration estimates [@zomerVersionGlobalAridity2022].
The aridity index is calculated as the ratio of mean annual precipitation to mean annual potential (or reference) evapotranspiration with values between 0 and 0.5 considered hyper to semi-arid, and values above 0.65 as humid.

@@

Our systematic review identified a total of 33 studies and 125 effect sizes on FIB, 24 studies and 50 effect sizes on TN, 31 studies and 88 effect sizes for DIN, 31 studies and 61 effect sizes for TP, 17 studies and 36 effect sizes for PO~4~, and 33 studies with 125 effect sizes for TSS. 
The majority of studies were identified as smaller scaled lot or field studies (Figure \@ref(fig:bmpsummary) A).
FIB studies had a roughly equal proportion of large watershed/catchment studies and studies conducted at the community/farm scale or smaller.
We also identified that the majority of studies (all parameters) were conducted on urban or non-agricultural runoff (Figure \@ref(fig:bmpsummary) B).
We did identify a wide variety of BMPs in the review, but it did not appear that any particular type of BMP was responsible for the majority of studies for any given parameter (Figure \@ref(fig:bmpsummary) C).
Our review was restricted to studies published from 2000 through 2022.
The number of studies published for each parameter were roughly uniformly distributed over time (Figure \@ref(fig:bmptemporal) A) and are not indicative of increases or decreases in the number of published studies.
Study length was strongly skewed for all parameters (Figure \@ref(fig:bmptemporal) B). Median study lengths were 3 (DIN), 2 (FIB), 2.5 (PO~4~), 2.5 (TN), 2.5 (TP), and 2 (TSS) years. 
There appears to be a strong clustering of BMP studies in the mid-Atlantic region (North Carolina, Virginia, Maryland) with other states sparsely represented or completely absent from the review (Figure \@ref(fig:studymap)).

@@

Study design prevented us from properly assessing BMP effectiveness as a function of age.
Conducting a meta-analysis of BMP effectiveness over time is hampered both by the lack of long-term studies and lack of standardized reporting mechanisms.
Some studies simply describe the change in pollutant concentrations or loads at the beginning and end of the study as a percent change [@haileHydraulicPerformancePollutant2016] which presents statistical problems, especially when sampling variance is not reported.
Changes in performance can also be described using a linear regression using date (transformed as a numeric variable) as an independent variable and log-transformed water quality as the dependent variable [@mitschCreatingWetlandsPrimary2012; @mitschValidationEcosystemServices2014; @pausAssessmentHydraulicToxic2014].
Slopes are a valid effect size for use in meta-analysis but the set of covariates used between studies should be the same since the coefficient of interest is adjusted to account for other terms in the regression model [@beckerSynthesisRegressionSlopes2007].
It would be reasonable to assume that regressions equations vary between studies to adjust results for seasonality, flow rates, and other variables.
Future efforts for assessing the performance of BMPs over time would benefit not only from more studies, but a more standardized method for providing comparable results.

@@

Raw data from the systematic review is deposited on Zenodo: https://zenodo.org/doi/10.5281/zenodo.8302472.
R code used in the analysis is also deposited on Zenodo: https://zenodo.org/records/10795231.

@@

```{r bmpsummary}
#| fig.cap: "Summary of (A) study scale and (B) dominant runoff source. Water quality parameters include total suspended sediment (TSS), total phosphorus (TP), total nitrogen (TN), orthophosphate (PO\\textsubscript{4}), fecal indicator bacteria (FIB), and dissolved inorganic nitrogen (DIN)."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r bmpsummaryparam}
#| fig.cap: "Summary BMPs identified in the systematic review by tested parameter. Water quality parameters include total suspended sediment (TSS), total phosphorus (TP), total nitrogen (TN), orthophosphate (PO\\textsubscript{4}), fecal indicator bacteria (FIB), and dissolved inorganic nitrogen (DIN)."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("../figures/bmp_summary_param.pdf")

```{r bmptemporal}
#| fig.cap: "Number of studies identified in the systematic review summarized by (A) publication date and (B) study length. Water quality parameters include total suspended sediment (TSS), total phosphorus (TP), total nitrogen (TN), orthophosphate (PO\\textsubscript{4}), fecal indicator bacteria (FIB), and dissolved inorganic nitrogen (DIN)."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r studymap}
#| fig.cap: "Distribution of studies identified in the systematic review by state and parameter. Water quality parameters include total suspended sediment (TSS), total phosphorus (TP), total nitrogen (TN), orthophosphate (PO\\textsubscript{4}), fecal indicator bacteria (FIB), and dissolved inorganic nitrogen (DIN)."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r overalleffect}
#| fig.cap: "Estimated effect sizes and intervals from the intercept only multilevel random effects model. Individual points represent studies, with size scaled by sampling variance. The point estimate with uncertaintity bars indicate the estimated overall effect, 95% confidence intervals, and 95% prediction intervals. Here, \\textit{k} indicates the number of overall effects with the number of unique studies in parenthesis. Water quality parameters include total suspended sediment (TSS), total phosphorus (TP), total nitrogen (TN), orthophosphate (PO\\textsubscript{4}), fecal indicator bacteria (FIB), and dissolved inorganic nitrogen (DIN)."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r fibeffect}
#| fig.cap: "Predicted marginal effect of influent fecal indicator bacteria (FIB; Panel A) and aridity index (conditioned on BMP subcategory; Panel B). Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance. Higher aridity index (mean annual precipition/evapotranspiration) indicates more humid conditions."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r phoseffect}
#| fig.cap: "Predicted marignal effect of influent pollutant concentration on total phosphorus (TP; Panel A) and orthophosphate (PO\\textsubscript{4}; Panel B) reductions. Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

@@

```{r aiindex}
#| fig.cap: "Comparison of the relative distributions (density) of aridity index values (mean annual precipition/evapotranspiration) across the U.S., across U.S. agricultural and developed land uses, and for BMP study locations. Higher aridity index values indicate more humid conditions."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "50%"
